%% start of file `jdoe_classic.tex'.
%% Copyright 2006 Xavier Danaux.
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[black]{classic}

\usepackage[utf8]{inputenc}
\usepackage{color}

% personal data
\firstname{Yu,}
%\familyname{Yue}
\title{University of Illinois at Chicago \newline \small{\texttt{\textbf{Homepage: {\color{web}\weblink{http://imyy.net}}}}}}
%\address{Office 719 SEO\\ 851 S. Morgan St.}{Chicago, IL}
\extrainfo{Office 719 SEO\\ 851 S. Morgan St.\\ Chicago, IL 60606}
\phone{540--yy--yueyu}
\email{yyu9 at uic.edu}
%\photo[64pt]{Yue_Yu}

\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}
\definecolor{web}{rgb}{0.2,0.2,0.2}
%\definecolor{web}{rgb}{0.5,0.5,0.5}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\section{\textbf{Education}}
\cventry{2007--Present}{\textbf{Master of Science in
Mathematics}}{University of Illinois at Chicago}{USA}{}{ - Expected
in SUMMER 2009.\newline - Concentrate in Probability and Statistics,
over all GPA: 4.0/4.0.}
\cventry{2003--2007}{\textbf{Bachelor of Science}}{Fudan
University}{China}{}{ - Major in Mathematics and Applied
Mathematics, last two years GPA: 3.4/4.0.}
\cvitem{---}{\textsc{Undergraduate Thesis}}
\cvitem{title}{\textit{Nonstatistical Methods for Credit Scoring and
Its Applications}} \cvitem{description}{Develop three strategies for
credit scoring: linear programming, genetic algorithm and
back--propagating neural network and three model is built in MATLAB
for real data in order to evaluate their performances.}

\section{\textbf{Academic Background}}
\cvitem{Mathematics}{Calculus, Mathematical Analysis, ODE \& PDE,
Complex Analysis, Real Analysis, Linear Algebra, Modern Algebra, Topology, ......}
\cvitem{Statistics}{Probability Theory, Statistical Theory, Applied Statistical Methods,
Sampling Theory, Linear Statistical Inference, Nonparametric Methods, Statistical Learning, ......}
\cvitem{Computing}{Programming Language Design, Parallel Computing, Data Mining and Prediction, Scientific Software, Numerical Analysis, ......}
\cvitem{Finance}{Managerial Finance, Derivatives Markets, Theory of Interest, ......}

\section{\textbf{Scholarships}}
\cventry{2006}{\textbf{People Scholarship}}{}{Fudan
University}{China}{} \cventry{2003--2006}{\textbf{Basic Science
Scholarship}}{}{Fudan University}{China}{}


\section{\textbf{Undergraduate Contest Awards}}
\cventry{Mar, 2007}{\textbf{Meritorious Winner}}{Interdisciplinary
Contest in Modeling}{}{}{ - Administered by the Consortium for
Mathematics and Its Applications, and sponsored by \newline \ \
SIAM, the NSA, and INFORMS.\newline - Webpage: {\color{web}
\weblink{http://www.comap.com/undergraduate/contests/icm/}}}
\cventry{Dec, 2006}{\textbf{Second Prize}}{China Undergraduate
Mathematical Contest in Modeling}{China}{}{} \cventry{Dec,
2005}{\textbf{Outstanding Award}}{Undergraduate Mathematical
Modeling Contest}{China}{}{ - The \textbf{1st} in East China.}
\cventry{Nov, 2002}{\textbf{Third Prize}}{Chinese Chemical
Olympiad}{China}{}{} \cventry{Oct, 2002}{\textbf{Second
Prize}}{Chinese Mathematical Olympiad}{China}{}{} \cventry{Dec,
2001}{\textbf{First Prize}}{Chinese Physics Olympiad}{China}{}{}
\cvitem{}{}
\cvitem{}{}


\section{\textbf{Experience}}
\subsection{\textbf{Working}}
\cventry{2009}{\textbf{Research Assistant}}{Technology Resources/Statistics, Epidemiology \& Surveillance}{Baxter Healthcare Corporation, Round Lake, IL}{}
{ - Serve as a contractor full time during summer and half time during the semester schedule.\newline
 - Perform under supervision for adverse event/product complaint surveillance; for R\&D animal studies, stability studies, reliability studies, manufacturing quality control studies; and for data analyses for clinical studies and related activities.}
\subsection{\textbf{Research}}
\cventry{2008}{\textbf{Statistical Lab}}{UIC}{}{}{
- Provid statistical consulting service for faculty, staff and graduate students inside or
outside the university.\newline
- Webpage: {\color{web} \weblink{http://www.math.uic.edu/\textasciitilde jyang06/statlab/StatLab.html}}}
\cventry{2007}{\textbf{Parallel Computing Lab}}{Fudan University}{}{}{
- Develop a parallel block reduction method for solving multiscale linear systems, use LAPACK and MPI
to build a package to perform the algorithm and evaluate its performance.}
%\cventry{Oct, 2006}{\textbf{L'Or$\mathbf{\acute{e}}$al e-Strat Challenge}}{China}{}{}{
%- Construct the main framework, and analyze R\&D segment, differentiate strategy for high--end and low--end product.}
\cventry{2004--2006}{\textbf{Mathematical Modeling Team Leader}}{Fudan University}{}{}{
- Lead a group of students with some Mathematical Modeling projects, make a two--hour presentation each season.}
\subsection{\textbf{Academia}}
\cventry{Oct. 2008}{\textbf{Fifth Midwest Database Research
Symposium}}{Chicago, Illinois}{}{}{} \cventry{May.
2008}{\textbf{The 31st Midwest Biopharmaceutical Statistics
Workshop}}{Muncie, Indiana}{}{}{}
\subsection{\textbf{Teaching}}
\cventry{2007--2008}{\textbf{Teaching Assistant}}{Department of Math, Stat, and CS}{\textit{UIC}}{}{
- Teach discussion sections for Math 121 -- Precalculus.}
\cventry{2004}{\textbf{Volunteer Teacher}}{China}{}{}{
- Two monthes volunteer teacher for rural ShanDong Province.}

\cventry{2006}{Translator}{}{}{}{Translated Ananth Grama lecture slides of \emph{Introduction to Parallel Computing}}
%\cventry{2003--2005}{Vice Chairman}{Visions of Science society}{Fudan University}{}{Manage the funds of the society and organize the %society's activities.}\\[-2pt]
\cventry{2004}{Volunteer teacher}{}{}{}{Two monthes volunteer teacher for rural ShanDong Province.}
\cventry{2004--2006}{Mathematics tutor}{}{}{}{Teaching seven high school students basic mathematics, answering any of their questions.}

\section{\textbf{Completion Actuarial Exams}}
\cventry{Nov, 2007}{\textbf{Exam P/1}}{Society of Actuaries}{}{}{}
\cventry{May, 2008}{\textbf{Exam FM/1}}{Society of Actuaries}{}{}{}

\section{\textbf{Languages}}
\cvlanguage{Chinese}{Native}{}
\cvlanguage{English}{Fluent}{
TOEFL(PBT) Score: 633/677, Essay rating: 4.5/6.0;\\
GRE Score: Verbal 540/800, Quantitive 800/800;\\
GRE Analytical Writing: 4.0/6.0.
}

\section{\textbf{Computer skills}}
\cvcomputer{OS}{Linux/Unix, Windows, DOS} {programming}{C/C++, Java, MPI,
Python, SQL}
\cvcomputer{job-related}{SAS, SAS Enterprise Guide, Minitab}{typography}{\LaTeX, Microsoft Office}
\cvcomputer{scientific}{Matlab, Maple, R, Lingo} {}{}

\section{\textbf{Scientific Interests}}
\cvlistitem{Statistical Learning}
\cvlistitem{Time Series Analysis}
\cvlistitem{Spatial Statistics}
\cvlistitem{Stochastic Process}
\cvlistitem{Data/Text Mining}
\cvlistitem{Boundary Value Problems}
\cvlistitem{Numerical Analysis}
\cvlistitem{Parallel Computing}
\end{document}
